The Nature and Orbit of the Ophiuchus Stream

### 2015-01-06 tex/ms.tex
Fixed the caption of Fig 11.
Rotated Table 4 so it does not bleed over the page.

\begin{figure}
\plotone{orbit_XYZ.pdf}
\caption{
The orbit of the Ophiuchus stream in the past 370 Myr (about one orbital
period), shown in a right-handed galactocentric Cartesian coordinate system.
In this coordinate system, the Sun is at $(X,Y,Z)=(8,0,0)$ kpc and the y-axis is
positive towards galactic longitude $l=90\arcdeg$. Note the pericenter passage
at $t\approx-250$ Myr (solid square). Near this point in time, the stream was
also passing through the disk ($Z\sim0$ kpc, see the top left panel) and was 
experiencing strong tidal forces due to disk shocking (see
Figure~\ref{tidal_force}).
\label{orbit_XYZ}}
\end{figure}

@@

@@

\begin{deluxetable*}{lrrrrrrrrrrr}
\tabletypesize{\scriptsize}
\setlength{\tabcolsep}{0.02in}
\tablecolumns{12}
\tablewidth{0pc}
\tablecaption{Ophiuchus Stream Member Stars\label{table1}}
\tablehead{
\colhead{Name} & \colhead{R.A.} & \colhead{Decl.} &
\colhead{$g_{P1}$} & \colhead{$r_{P1}$} & \colhead{$i_{P1}$} &
\colhead{$z_{P1}$} & \colhead{$y_{P1}$} &
\colhead{$v_{los}$} & \colhead{DM} &
\colhead{$\mu_l$} & \colhead{$\mu_b$} \\
\colhead{ } & \colhead{(deg)} & \colhead{(deg)} &
\colhead{(mag)} & \colhead{(mag)} & \colhead{(mag)} &
\colhead{(mag)} & \colhead{(mag)} &
\colhead{(km s$^{-1}$)} & \colhead{(mag)} &
\colhead{(mas yr$^{-1}$)} & \colhead{(mas yr$^{-1}$)}
}
\startdata
bhb1 & 241.52271 & -7.01555 & $16.05\pm0.02$ & $16.11\pm0.02$ & $16.22\pm0.01$ & $16.25\pm0.02$ & $16.25\pm0.02$ & $286.7\pm1.8$ & $14.84_{-0.02}^{+0.03}$ & $-2.4\pm2.0$ & $0.5\pm1.5$ \\
bhb2 & 241.49994 & -7.03409 & $16.02\pm0.02$ & $16.09\pm0.02$ & $16.21\pm0.02$ & $16.25\pm0.02$ & $16.23\pm0.02$ & $285.3\pm1.9$ & $14.85_{-0.03}^{+0.03}$ & $-2.4\pm1.8$ & $-0.1\pm1.6$ \\
bhb3 & 242.13551 & -6.87785 & $15.96\pm0.02$ & $15.99\pm0.01$ & $16.11\pm0.02$ & $16.16\pm0.02$ & $16.13\pm0.02$ & $290.0\pm1.8$ & $14.71_{-0.02}^{+0.03}$ & $-7.4\pm2.0$ & $4.0\pm1.6$ \\
bhb4 & 241.94714 & -6.88995 & $16.22\pm0.02$ & $16.32\pm0.01$ & $16.48\pm0.02$ & $16.54\pm0.02$ & $16.56\pm0.02$ & $291.3\pm2.2$ & $14.74_{-0.02}^{+0.03}$ & $-4.3\pm1.9$ & $4.6\pm1.6$ \\
bhb6 & 242.33018 & -6.84405 & $15.67\pm0.01$ & $15.64\pm0.01$ & $15.59\pm0.01$ & $15.60\pm0.02$ & $15.54\pm0.02$ & $290.8\pm1.5$ & $14.67_{-0.02}^{+0.03}$ & $-2.5\pm1.8$ & $6.8\pm1.7$ \\
bhb7 & 242.91469 & -6.69329 & $15.66\pm0.01$ & $15.56\pm0.02$ & $15.57\pm0.01$ & $15.54\pm0.02$ & $15.50\pm0.02$ & $289.8\pm1.5$ & $14.55_{-0.03}^{+0.04}$ & $-5.9\pm2.0$ & $8.3\pm1.6$ \\
\hline
bhb6 & & & & & & & & $289.8\pm0.8$ & & & \\
rgb1 & 241.51689 & -6.98511 & $17.71\pm0.02$ & $17.18\pm0.02$ & $16.91\pm0.02$ & $16.78\pm0.02$ & $16.71\pm0.02$ & $286.0\pm0.8$ & $14.84_{-0.03}^{+0.03}$ & $-4.9\pm2.0$ & $-0.1\pm1.8$ \\
rgb2 & 241.94649 & -6.86113 & $17.34\pm0.02$ & $16.74\pm0.02$ & $16.46\pm0.02$ & $16.32\pm0.02$ & $16.25\pm0.02$ & $286.7\pm0.6$ & $14.74_{-0.02}^{+0.03}$ & $-6.1\pm2.1$ & $2.7\pm1.7$ \\
rgb3 & 241.96089 & -6.89873 & $17.64\pm0.02$ & $17.08\pm0.02$ & $16.83\pm0.02$ & $16.68\pm0.02$ & $16.62\pm0.02$ & $287.5\pm0.7$ & $14.74_{-0.02}^{+0.03}$ & $-6.5\pm2.0$ & $3.8\pm1.8$ \\
rgb4 & 242.26139 & -6.90190 & $17.05\pm0.02$ & $16.45\pm0.02$ & $16.17\pm0.01$ & $16.02\pm0.02$ & $15.93\pm0.02$ & $288.8\pm0.5$ & $14.70_{-0.02}^{+0.03}$ & $-30.0\pm1.8$ & $-19.1\pm1.5$ \\
rgb5 & 242.14832 & -6.79765 & $17.79\pm0.02$ & $17.23\pm0.02$ & $16.96\pm0.02$ & $16.82\pm0.02$ & $16.74\pm0.02$ & $288.0\pm0.9$ & $14.69_{-0.02}^{+0.03}$ & $-6.8\pm2.1$ & $-0.6\pm1.9$ \\
sgb1 & 241.95962 & -6.86881 & $18.90\pm0.02$ & $18.53\pm0.02$ & $18.38\pm0.02$ & $18.31\pm0.02$ & $18.28\pm0.02$ & $289.4\pm2.2$ & $14.74_{-0.02}^{+0.03}$ & $-6.5\pm3.0$ & $-0.2\pm2.3$ \\
msto1 & 242.02040 & -6.84122 & $19.22\pm0.02$ & $18.89\pm0.02$ & $18.74\pm0.02$ & $18.69\pm0.02$ & $18.62\pm0.03$ & $291.8\pm2.2$ & $14.72_{-0.02}^{+0.03}$ & $-9.3\pm3.2$ & $6.8\pm2.8$ \\
msto2 & 242.18360 & -6.84056 & $19.10\pm0.02$ & $18.70\pm0.02$ & $18.54\pm0.02$ & $18.45\pm0.02$ & $18.42\pm0.03$ & $286.4\pm2.6$ & $14.70_{-0.02}^{+0.03}$ & $-6.1\pm3.0$ & $3.7\pm2.5$
\enddata
\tablecomments{The horizontal line separates stars observed by DEIMOS and
Hectochelle. The name indicates the likely evolutionary stage inferred from
isochrone fitting. The PS1 photometry is {\em not} corrected for extinction. The
uncertainty in $v_{los}$ includes the uncertainty from cross-correlation/fitting
and the uncertainty in the zero-point of wavelength calibration. The DM
indicates the average DM of the stream at the position of the star, and
the uncertainties are $68\%$ confidence limits. The proper motion in the
galactic longitude direction, $\mu_l$, includes the $\cos b$ term.}
\end{deluxetable*}

>>>>

\begin{figure}
\plotone{orbit_XYZ.pdf}
\caption{
The orbit of the Ophiuchus stream in the past 370 Myr (about one orbital
period), shown in a right-handed galactocentric Cartesian coordinate system.
In this coordinate system, the Sun is at $(X,Y,Z)=(8,0,0)$ kpc and the y-axis is
positive towards galactic longitude $l=270\arcdeg$. Note the pericenter passage
at $t\approx-250$ Myr (solid square). Near this point in time, the stream was
also passing through the disk ($Z\sim0$ kpc, see the top left panel) and was 
experiencing strong tidal forces due to disk shocking (see
Figure~\ref{tidal_force}).
\label{orbit_XYZ}}
\end{figure}

@@

\newpage

\begin{turnpage}
\begin{deluxetable*}{lrrrrrrrrrrr}
\tabletypesize{\scriptsize}
\setlength{\tabcolsep}{0.02in}
\tablecolumns{12}
\tablewidth{0pc}
\tablecaption{Ophiuchus Stream Member Stars\label{table1}}
\tablehead{
\colhead{Name} & \colhead{R.A.} & \colhead{Decl.} &
\colhead{$g_{P1}$} & \colhead{$r_{P1}$} & \colhead{$i_{P1}$} &
\colhead{$z_{P1}$} & \colhead{$y_{P1}$} &
\colhead{$v_{los}$} & \colhead{DM} &
\colhead{$\mu_l$} & \colhead{$\mu_b$} \\
\colhead{ } & \colhead{(deg)} & \colhead{(deg)} &
\colhead{(mag)} & \colhead{(mag)} & \colhead{(mag)} &
\colhead{(mag)} & \colhead{(mag)} &
\colhead{(km s$^{-1}$)} & \colhead{(mag)} &
\colhead{(mas yr$^{-1}$)} & \colhead{(mas yr$^{-1}$)}
}
\startdata
bhb1 & 241.52271 & -7.01555 & $16.05\pm0.02$ & $16.11\pm0.02$ & $16.22\pm0.01$ & $16.25\pm0.02$ & $16.25\pm0.02$ & $286.7\pm1.8$ & $14.84_{-0.02}^{+0.03}$ & $-2.4\pm2.0$ & $0.5\pm1.5$ \\
bhb2 & 241.49994 & -7.03409 & $16.02\pm0.02$ & $16.09\pm0.02$ & $16.21\pm0.02$ & $16.25\pm0.02$ & $16.23\pm0.02$ & $285.3\pm1.9$ & $14.85_{-0.03}^{+0.03}$ & $-2.4\pm1.8$ & $-0.1\pm1.6$ \\
bhb3 & 242.13551 & -6.87785 & $15.96\pm0.02$ & $15.99\pm0.01$ & $16.11\pm0.02$ & $16.16\pm0.02$ & $16.13\pm0.02$ & $290.0\pm1.8$ & $14.71_{-0.02}^{+0.03}$ & $-7.4\pm2.0$ & $4.0\pm1.6$ \\
bhb4 & 241.94714 & -6.88995 & $16.22\pm0.02$ & $16.32\pm0.01$ & $16.48\pm0.02$ & $16.54\pm0.02$ & $16.56\pm0.02$ & $291.3\pm2.2$ & $14.74_{-0.02}^{+0.03}$ & $-4.3\pm1.9$ & $4.6\pm1.6$ \\
bhb6 & 242.33018 & -6.84405 & $15.67\pm0.01$ & $15.64\pm0.01$ & $15.59\pm0.01$ & $15.60\pm0.02$ & $15.54\pm0.02$ & $290.8\pm1.5$ & $14.67_{-0.02}^{+0.03}$ & $-2.5\pm1.8$ & $6.8\pm1.7$ \\
bhb7 & 242.91469 & -6.69329 & $15.66\pm0.01$ & $15.56\pm0.02$ & $15.57\pm0.01$ & $15.54\pm0.02$ & $15.50\pm0.02$ & $289.8\pm1.5$ & $14.55_{-0.03}^{+0.04}$ & $-5.9\pm2.0$ & $8.3\pm1.6$ \\
\hline
bhb6 & & & & & & & & $289.8\pm0.8$ & & & \\
rgb1 & 241.51689 & -6.98511 & $17.71\pm0.02$ & $17.18\pm0.02$ & $16.91\pm0.02$ & $16.78\pm0.02$ & $16.71\pm0.02$ & $286.0\pm0.8$ & $14.84_{-0.03}^{+0.03}$ & $-4.9\pm2.0$ & $-0.1\pm1.8$ \\
rgb2 & 241.94649 & -6.86113 & $17.34\pm0.02$ & $16.74\pm0.02$ & $16.46\pm0.02$ & $16.32\pm0.02$ & $16.25\pm0.02$ & $286.7\pm0.6$ & $14.74_{-0.02}^{+0.03}$ & $-6.1\pm2.1$ & $2.7\pm1.7$ \\
rgb3 & 241.96089 & -6.89873 & $17.64\pm0.02$ & $17.08\pm0.02$ & $16.83\pm0.02$ & $16.68\pm0.02$ & $16.62\pm0.02$ & $287.5\pm0.7$ & $14.74_{-0.02}^{+0.03}$ & $-6.5\pm2.0$ & $3.8\pm1.8$ \\
rgb4 & 242.26139 & -6.90190 & $17.05\pm0.02$ & $16.45\pm0.02$ & $16.17\pm0.01$ & $16.02\pm0.02$ & $15.93\pm0.02$ & $288.8\pm0.5$ & $14.70_{-0.02}^{+0.03}$ & $-30.0\pm1.8$ & $-19.1\pm1.5$ \\
rgb5 & 242.14832 & -6.79765 & $17.79\pm0.02$ & $17.23\pm0.02$ & $16.96\pm0.02$ & $16.82\pm0.02$ & $16.74\pm0.02$ & $288.0\pm0.9$ & $14.69_{-0.02}^{+0.03}$ & $-6.8\pm2.1$ & $-0.6\pm1.9$ \\
sgb1 & 241.95962 & -6.86881 & $18.90\pm0.02$ & $18.53\pm0.02$ & $18.38\pm0.02$ & $18.31\pm0.02$ & $18.28\pm0.02$ & $289.4\pm2.2$ & $14.74_{-0.02}^{+0.03}$ & $-6.5\pm3.0$ & $-0.2\pm2.3$ \\
msto1 & 242.02040 & -6.84122 & $19.22\pm0.02$ & $18.89\pm0.02$ & $18.74\pm0.02$ & $18.69\pm0.02$ & $18.62\pm0.03$ & $291.8\pm2.2$ & $14.72_{-0.02}^{+0.03}$ & $-9.3\pm3.2$ & $6.8\pm2.8$ \\
msto2 & 242.18360 & -6.84056 & $19.10\pm0.02$ & $18.70\pm0.02$ & $18.54\pm0.02$ & $18.45\pm0.02$ & $18.42\pm0.03$ & $286.4\pm2.6$ & $14.70_{-0.02}^{+0.03}$ & $-6.1\pm3.0$ & $3.7\pm2.5$
\enddata
\tablecomments{The horizontal line separates stars observed by DEIMOS and
Hectochelle. The name indicates the likely evolutionary stage inferred from
isochrone fitting. The PS1 photometry is {\em not} corrected for extinction. The
uncertainty in $v_{los}$ includes the uncertainty from cross-correlation/fitting
and the uncertainty in the zero-point of wavelength calibration. The DM
indicates the average DM of the stream at the position of the star, and
the uncertainties are $68\%$ confidence limits. The proper motion in the
galactic longitude direction, $\mu_l$, includes the $\cos b$ term.}
\end{deluxetable*}
\end{turnpage}

@@

\global\pdfpageattr\expandafter{\the\pdfpageattr/Rotate 90}
